Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2017-12-18 article/ms.tex
introduced poster children scrappy

\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

@@

\textit{The Cannon}, a data based spectral model devloped by \cite{ho2017}, was fitted to each star in the spectra based around each star's $T_{eff}$, log(g), [Fe/H] and [$\alpha$/M].
%Ho2017 says that using Appogee, they found almost 10000 giants which were common between the lamost and apoggeee surveys and used that to fit a predictive model to the lamost giants (450000) to determine the 'Teff, logg, [Fe/H], and [α/M]'.
This model is treated as representative of the expected spectra for each star.

@@

>>>>

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}

\usepackage{color}
\usepackage{booktabs,chemformula}
\usepackage[export]{adjustbox}

\usepackage{tabularx}

\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}

\usepackage{tikz}
\usepackage{hyperref}

@@

\textit{The Cannon}, a data based spectral model devloped by \cite{ho2017} using APOGEE data, was fitted to each star in our 450000 star sample of LAMOST giants.
%Ho2017 says that using Appogee, they found almost 10000 giants which were common between the lamost and apoggeee surveys and used that to fit a predictive model to to lamost giants (450000) to determine the 'Teff, logg, [Fe/H], and [α/M]'.
This model is treated as representative of the expected spectra for each star.

@@

\begin{figure}
\centering
\begin{subfigure}{.5\linewidth}
  \centering
  \includegraphics[width=.95\linewidth]{29277_Mg}
  \caption{Mg}
  \label{Mgposter}
\end{subfigure}%       %Note: the % to the left is VERY IMPORTANT.

\begin{subfigure}{.5\linewidth}
  \centering
  \includegraphics[width=.95\linewidth]{29277_K}
  \caption{K}
  \label{Kposter}
\end{subfigure}
\caption{}
\label{posterchildren}
\end{figure}
